Practical Optional Types for Clojure

### 2015-02-24 overview.tex
clojure reference

Clojure~\cite{something-for-clojure} is a Lisp built to run on the
Java Virtual Machine with exemplary support for concurrent programming
and immutable data structures. It emphaisizes mostly-functional
programming, restricting imperative updates to a limited set of
structures which have specific thread synchronization behavior. By
default, it provides fast implemenations of immutable lists, vectors,
and hash tables, which are used for most data structures, although it
also provides means for defining new records.

>>>>

Clojure~\cite{Hic08} is a Lisp built to run on the
Java Virtual Machine with exemplary support for concurrent programming
and immutable data structures. It emphaisizes mostly-functional
programming, restricting imperative updates to a limited set of
structures which have specific thread synchronization behavior. By
default, it provides fast implemenations of immutable lists, vectors,
and hash tables, which are used for most data structures, although it
also provides means for defining new records.
